The Forecast Trap

### 2022-04-12 manuscript/round4-manuscript.Rmd
no renv, old rtciles for correct csl use

---
title: "The Forecast Trap"
name: Carl Boettiger
email: "cboettig@berkeley.edu"
affiliation: a,1
date: "`r Sys.Date()`"

@@

csl: csl/ecology-letters.csl
output: rticles::elsevier_article
layout: 3p
journal: Ecology Letters
---

@@

I shall focus on examples involving fisheries management to illustrate principles shared in many ecological systems.
Fisheries are a significant economic and conservation concern worldwide and their management remains an important debate [e.g. @Worm2006; @Worm2009; @Costello2016].
Moreover, fisheries management has been a proving grounds for theoretical and practical decision-making issues [e.g. @Clark1973; @Reed1979; @Walters1981; @Ludwig1982] arising in a wide range of other contexts, including
invasive species [@Boettiger2021], infectious diseases [@Li2017; Shea2014], fire management [@Richards1999] conservation planning and prioritization [@Chades2008; @Wilson2006] climate policy [@Nitzbon2017] and much else [@Ludwig1993; @Lande1994; @Polasky2011].

>>>>

---
title: "The Forecast Trap"
name: Carl Boettiger
email: "cboettig@berkeley.edu"
affiliation: a,1
date: "`r Sys.Date()`"
csl: csl/ecology-letters.csl

@@

output: rticles::elsevier_article
layout: 3p
journal: Ecology Letters
---

@@

I shall focus on examples involving fisheries management to illustrate principles shared in many ecological systems.
Fisheries are a significant economic and conservation concern worldwide and their management remains an important debate [e.g. @Worm2006; @Worm2009; @Costello2016].
Moreover, fisheries management has been a proving grounds for theoretical and practical decision-making issues [e.g. @Clark1973; @Reed1979; @Walters1981; @Ludwig1982] arising in a wide range of other contexts, including
invasive species [@Boettiger2021], infectious diseases [@Li2017; @Shea2014], fire management [@Richards1999] conservation planning and prioritization [@Chades2008; @Wilson2006] climate policy [@Nitzbon2017] and much else [@Ludwig1993; @Lande1994; @Polasky2011].
